---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
    latex_engine: xelatex
---

```{r rsetup,eval=TRUE,include=FALSE}
require("codecheck")
require("knitr")
require("rprojroot")
require("yaml")
require("xtable")
require("tibble")
require("readr")
options(width = 60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r manifest, eval=TRUE, include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

manifest_df = copy_manifest_files(root, metadata,
                                  dest_dir, keep_full_path = FALSE,
                                  overwrite = FALSE
                                  )
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(metadata, manifest_df, root)
```

# Summary

I could reproduce the Quarto document that generated all the figures
that were found in the paper.  It was however not straightforward for
two reasons:

1.  Although the R packaging ecosystem is good, with so many
    dependencies there can be edge cases to resolve manually.  In
    this case, as noted in the comments of the document, I had a
    problem with "lme4", so followed the advice in the document.  I
    also had an issue with one of the packages on github.

2.  I hit an error within the Rmd that I was unable to fix; luckily,
    removing that code chunk had no negative effect on the rest of the
    document compiling.
	
Otherwise, the document compiled. I am grateful to the authors'
clear instructions on reducing the computation time by reducing the
number of samples to simulate.

\clearpage

# CODECHECKER notes

I found the code and data to be clearly arranged, and this promised to
be a very quick codecheck based on my experience of working with other
projects from this research group.

As noted in the summary though, I did hit some issues, but fortunately
I could resolve them myself.

## Preliminaries

To start I moved the original figures and html:
```{sh eval=FALSE}
 cp PowerCalc.html PowerCalc-orig.html
 mv Figures Figurees-orig
 mkdir Figures
```

## Reducing computation time

The authors provided a clear mechanism for reducing the computation
time for sampling (related to Figure 4).  I therefore changed line 15
of the quarto doc to read:

```
  n_samples: 10
```

## Installation steps

I liked the use of pacman, a package I'd not seen before, for the
on-demand installation of packages.  Perhaps the only oddity was that
it didn't tag the versions of the packages that were required.

### Installation of lme4

The first error I hit was that lme4 package was causing errors.  The
authors did note that this might be an issue, and so I simply ran the
following, as suggested:

```{r eval=FALSE}
oo <- options(repos = "https://cran.r-project.org/")
install.packages("Matrix", type = "source")
install.packages("lme4", type = "source")
options(oo)
library(lme4)
library(lmerTest)
```

### Installation of loglightR

I could not get the group's package to install from github:

```{r eval=FALSE}
> p_load_gh(char = packages_github)
```



generated the error:

```
Error in utils::download.file(url, path, method = method, quiet = quiet,  : 
  download from 'https://api.github.com/repos/tscnlab/LightLogR/tarball/HEAD' failed
Warning messages:
1: In p_install_gh(package, dependencies, ...) :
  The following may have incorrect capitalization specification:

LightLogR
2: In p_load_gh(char = packages_github) : 
Failed to install/load:
tscnlab/LightLogR
```

Luckily, I was able to use the version available on CRAN, which worked
fine:

```{r eval=FALSE}
install.packages("LightLogR")
```


## Running the code

Once package dependencies were satisfied, most of the code worked fine
until this snippet:

```{r eval=FALSE}
> Nonwear_summary %>%
+ gtsummary::tbl_summary(
+ statistic = list(NonWear ~"{min} - {max}"),
+ label = list(NonWear ~ "Non-Wear Time",
+ valid_Day ~ "Valid Days"),
+ by = valid_Day)
Error in `gtsummary::tbl_summary()`:
! Error processing `label` argument.
! Can't select columns that don't exist. ✖ Column `valid_Day` doesn't exist.
ℹ Select among columns "Id", "Season", "Day", and "NonWear"
Run `rlang::last_trace()` to see where the error occurred.

> colnames(Nonwear_summary)
[1] "Id"        "Season"    "Day"       "NonWear"   "valid_Day"
```

I am not expert enough in the tidyverse to see why this error was
generated.  Further, I needed to use `rmarkdown::render` to render the
document, rather than quarto, so that I could do some debugging.  I
found:

I therefore gave up, changed the chunk to the following, and
pressed-on.


```{r eval=FALSE}
Nonwear_summary %>% 
  gtsummary::tbl_summary(
    statistic = list(NonWear ~"{min} - {max}"),
    label = list(NonWear ~ "Non-Wear Time"),
    ##valid_Day ~ "Valid Days"),
    by = valid_Day)
```

By luck, the document then compiled.  I concluded that rendering this
problematic table was not required for the rest of the computation.

Visual comparison of my version of the  figures with their versions
showed that we had reproduced all the  manuscript Figures.  The only
difference I observed was that my Figure 4 showed much more variance
than their Figure 4.  This is entirely expected given I only ran 10
samples, rather than 1000.

## Computation time

I ran this on a MacBook Pro M1 laptop; once all packages were
installed, it took maybe 5-10 minutes to compile.


## Highlights

1. I liked the clear instructions and mechanisms for reducing the
   number of samples required.

2. The code vignette generated the "camera ready" figures that
   appeared in the publication.  (Often times in other work there is
   manual post-processing of Figures before including them in the manuscript.

2. Excellent to see quarto now being used for such projects.  (It has
   spurred me on to plan a rewrite of codecheck infrastructure to move
   away from Rmd to quarto.)


## Recommendations

Here are some comments if the authors are interested in the 'next
level' in reproducibility.

1. Trivial point: your readme didn't tell someone who is new to Quarto
   exactly how to render the document.

2. Consider use of renv (has been done before in the research group)
for stating package dependencies.

3. Convert the code repository into an R package;  in this way, by
running something like:

```{R eval=FALSE}
remotes::install_package("tcnslab/...")
```
might help you with installation issues (or it might not).  But having
a package for a significant body of work like this would make things
tidy.

5. Adding the following to the end of a quarto document will document
   what environment you compiled your work in.  See for example the
   end of this document for what it generates:

```{r eval=FALSE}
sessionInfo()
```

\clearpage


# Manifest files

```{r, echo=FALSE, results="asis", width=100}
for(i in c(1:nrow(manifest_df))) {
  path <- manifest_df[i,"dest"]
  if(stringr::str_ends(path, "(png|pdf|jpg|jpeg)")) {
    # include graphics with knitr has to happen at top level in chunks, see https://github.com/yihui/knitr/issues/1260
    # see also https://stackoverflow.com/questions/51268623/insert-images-using-knitrinclude-graphics-in-a-for-loop
    # knitr::include_graphics(manifest_df[1, "dest"], error = TRUE)
    # Therefore, generate Markdown code here:
    cat("## ", basename(path), "\n\n")
    cat("**Comment:** ", manifest_df[i,"comment"], "\n\n")
    cat(paste0("![", "Test ", "](", path, ")\n"))
  } else if (stringr::str_ends(path, "(Rout|txt)")) {
    cat("## ", basename(path), "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    cat(readLines(path), sep = "\n")
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "csv")) {
    cat("## ", basename(path), "\n\n", "Summary statistics of tabular data:", "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    print(skimr::skim(read.csv(path)))
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else {
    cat("## ", basename(path), "\n\n")
    cat("Cannot inlcude output file as figure.")
  }
  
  cat("\\clearpage \n\n")
}
```

\clearpage

## Acknowledgements

I would like to thank Dr Bhatt and his team for promptly answering any
queries I had with this reproduction.  CODECHECK is financially
supported by the Mozilla foundation.

# Citing this document

```{r, results='asis',echo=FALSE}
cite_certificate(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently
reproduce the results of a computational analysis given the data and
code from a third party.  A CODECHECK does not check whether the
original computation analysis is correct.  However, as all materials
required for the reproduction are freely available by following the
links in this document, the reader can then study for themselves the
code and data.


# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{sh eval=TRUE}
quarto --version
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document") 
```
